\begin{rubric}{Grants}
\subrubric{Successful}

\entry*[2023] \textbf{HFSP, Research Grant} (\$1,350,000), co-I.
	\par \footnotesize "Quantifying The 4-dimensional Microenvironment To Explain The Coexistence Of Social Insects." \normalsize
\entry*[2023] \textbf{Durham University, Seedcorn Fund} (£15,000), PI.
	\par \footnotesize "Rewilding microclimates to conserve UK biodiversity under climate change." \normalsize
\entry*[2022] \textbf{Royal Geographical Society, Small Research Grant} (£2,960), PI.
	\par \footnotesize "Investigating the microclimate niche of threatened Omani plant species in the Western Hajar Mountains." \normalsize
\entry*[2022] \textbf{Anglo-Omani Society} (£6,000), co-I.
	\par \footnotesize "Investigating the microclimate niche of threatened Omani plant species in the Western Hajar Mountains." \normalsize
\entry*[2021] \textbf{HMEI internship funding} (USD \$6,600), to host an intern in summer 2021.
\entry*[2018] \textbf{ACCE Extension for Publication} (£3,600), to prepare \& submit a high impact manuscript.
\entry*[2018] \textbf{British Ecological Society, Travel Grant} (£500), to attend ATBC Annual Meeting.
\entry*[2016] \textbf{ACCE Placement Support} (£1,500), 3-month placement at Rewilding Britain, UK.
\entry*[2016] \textbf{Departmental Travel Fund} (£800), to attend Conservation Asia 2016.
\entry*[2014] \textbf{NERC, Doctoral Training Partnership studentship}, stipend (£55,452), research and training grant (£11,000) and fees (£17,484).
\entry*[2013] \textbf{Durham Fund (£1,000)}, for UNEP-WCMC internship.
%\entry*[2011] \textbf{£1,300} from various sources for Peruvian Amazon expedition.

%\subrubric{Pending}
%
%\entry*[2024] \textbf{Royal Society, Research Grant} (£20,000), PI.
%	\par \footnotesize "Using drone-based LiDAR to measure and model the 3D microclimate space of UK rewilding sites." \normalsize
%\entry*[2024] \textbf{NERC, Pushing the Frontiers} (£1,000,000.00), co-I.
%	\par \footnotesize "Revealing the mechanisms driving species responses to climate change (RESPONSE)." \normalsize

\subrubric{Unsuccessful}

\entry*[2024] \textbf{Rewilding Britain, Rewilding Innovation Fund} (£15,000), PI.
	\par \footnotesize "The Rewilding Microclimate Project." \normalsize
\entry*[2023] \textbf{NERC, Pushing the Frontiers} (£950,443), PI.
	\par \footnotesize "Redefining Extinction Risk Due To Climate Change." \normalsize
\entry*[2023] \textbf{NERC, Centre for Doctoral Training} (£2,437,344), co-I.
	\par \footnotesize "MargInal Lands and Ecosystem Services (MILES) in a period of rapid change." \normalsize
\entry*[2023] \textbf{NERC, Large Grant} (£526,258), co-I.
	\par \footnotesize "The Forgotten Forests: Uncovering The Potential Of Wet Woodlands As Nature Based Solutions." \normalsize
\entry*[2022] \textbf{British Ecological Society, Small Research Grant} (£4,970), PI.
	\par \footnotesize "Investigating the microclimate niche of threatened Omani plant species in the Western Hajar Mountains." \normalsize
\entry*[2022] \textbf{Woodland Trust, Small Research Grant} (£58,962), co-I.
	\par \footnotesize "Effective landscape-scale management tools for established and establishing woodlands." \normalsize
\entry*[2022] \textbf{Global Partnerships Seedcorn Fund} (£41,834), co-I.
	\par \footnotesize "NI RAP-THERM: Rapid Thermal Ecology Using Next Generation Technology." \normalsize
\entry*[2020] \textbf{NERC, Independent Reasearch Fellowship} (£598,358), PI.
	\par \footnotesize "Redefining extinction risk due to climate change." \normalsize
\end{rubric}