\renewcommand\labelitemi{$\diamond$}

\begin{rubric}{Research and Other Relevant Experience}
\entry*[2019 -- $\cdots\cdot$]%
	\textbf{Postdoctoral Researcher}, Princeton University, USA.
	\begin{itemize}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
	\item PI: Prof David Wilcove
	\item Exploring the effectiveness of different conservation strategies for recovering threatened species
	\end{itemize}
\entry*[2019]%
	\textbf{Postdoctoral Researcher}, University of Florida, USA.
	\begin{itemize}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
	\item PI: Dr Brett Scheffers
	\item The global distribution of colourful birds and its relevance for the conservation of aesthetically appealing species
	\end{itemize}
\entry*[2016]%
	\textbf{Knowledge Transfer Executive}, Rewilding Britain, UK.
	\begin{itemize}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
	\item Synthesising scientific \& grey literature to produce guidelines for applying rewilding at small scale
	\item Responding to public \& media requests for rewilding guidance
	\item Organising \& reporting on a stakeholder workshop on rewilding in the English uplands \parencite{sandom_rewilding_2018}
	\end{itemize}
\entry*[2014]%
	\textbf{Research Assistant} to Prof David Edwards, University of Sheffield, UK.
	\par Fieldwork in Bornean rainforest:
	\begin{itemize}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
	\item Tree-liana interaction networks \parencite{magrach_selective_2016}
	\item Quantifying microclimates using thermal cameras \parencite{scheffers_extreme_2017}
	\end{itemize}
\entry*[2013 -- 2014]%
	\textbf{Consultant.} UNEP-WCMC, Cambridge, UK.
	\begin{itemize}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
	\item Updating \& analysing UNEP-WCMC Google Scholar profile
	\item Incorporation of fisheries data into the Madingley model (\url{www.madingleymodel.org})
	\end{itemize}
\entry*[2013]%
	\textbf{Intern in the Science programme.} UNEP-WCMC, Cambridge, UK.
	\par Various contribution to the PREDICTS project (\url{www.predicts.org.uk}) and associated publications \parencite{newbold_global_2015, hudson_predicts_2014, hudson_database_2017}: 
	\begin{itemize}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
	\item Sensitivity analyses (part of R package development)
	\item Collation and analysis of trait data
	\item Species richness maps using spatial data from the IUCN Red List
	\end{itemize}
%\entry*[2011]%
%	\textbf{Young Explorer.} Peruvian Amazon expedition with British Exploring, UK.
%	\par Assisting in data collection for caiman, mammal \& bird  surveys
%
\end{rubric}